---
title: "Testing"
author: "Nokkvi Dan @NetApp"
date: "5/19/2021"
output: html_document
---

# About data:

Monitoring: Silixa's Carina Sensing system
Fiber optic cable: ConstellationTM fiber permanently cemented into well 78-32

Well 78-32: 3274.48 feet (1200 feet into granitoid basement rocks)
Dates: 04/14/2019 - 05/03/2019
Silixa-data detected 40 microseismic events between -1.5 to 0.5 M

version:    version of what ?
data:       signal of each trace  [1:30000, 1:1088]
traces:     traces
depth:      depth                 (ns) [1:30000]
pos:        position              (meters) [1:1088]
time0:      the time at which the transmitter starts to emit the wave
time:       time i+1 counter      (counter on depth)
surveymode: reflection            "char"
date:       "2019-04-19"


## Code:

```{r}
library(RGPR)
library(RSEIS)
library(rgdal)
library(tidyr)
```

# Importing data and subsetting

## Importing

```{r,warning=FALSE}
# Path to our file
Lname  <-  list.files(path='/Users/nokkvi/Git/SEGY', pattern="testdata", full.names=TRUE)

#reading the .sgy file - day1
gpr_data_day1 <- readGPR(Lname)
```

## Subset
```{r}
# Subsetting data so we have something to work with
gpr_df <- gpr_data_day1[c(1:30),c(1:10)]
```

```{r}
# function to change gpr_df to long format
gpr_df_long <- function(gpr_df){
  # taking the data
  df <- as.data.frame(gpr_df@data)
  
  # changing in to long format
  df_long <- gather(df, factor_key = TRUE)
  
  # setting parameters
  r <- nrow(df)
  c <- ncol(df)
  k <- nrow(df_long)
  
  # adding depth to long format
  df_long$depth <- rep(gpr_df@depth, times=c, each=1)
  df_long
}
```

```{r}
# changing gpr_df -> gpr_df_long
source <- gpr_df_long(gpr_df)
```

# Basic processing steps

## Plot
```{r}
#if(!require("devtools")) install.packages("devtools")
#devtools::install_github("emanuelhuber/RGPR")
```

```{r}
# Plotting the whole dataset
#plot(x)
```

## First wave break and time zero estimation

**THE EASY WAY:** ´x <- estimateTime0(x, w = 20, method = "coppens", thr = 0.05, FUN = mean)`

Here, we define time-zero, $t_0$ as the time at which the transmitter starts to emit the wave.

Maybe is time zero not correctly set. To get the time-zero for each traces of x use the function time0().

The first wave break $t_{fb}$ is estimated for each traces and it's the time of the first wave record:

```{r}
# time of the first wave record
#tfb <- firstBreak(xx, w = 20, method = "coppens", thr = 0.05)
# plot of tfb
#plot(pos(xx), tfb, pch = 20, ylab = "first wave break", xlab = "position (m)")
```

Convert the first wave break time $t_{fb}$ into time zero $t_0$ with firstBreakToTime0(). In math it is $t_0 = t_{fb} - \frac{a}{c_0}$

a= distance between transmitter and reciver
$c_0$

```{r}
# creating a vectpr
#t0 <- firstBreakToTime0(tfb, xx)

# set time0
#time0(xx) <- t0
```

Note:

* If t0 is too noisy, you can set time0(x) = mean(t0)

The change of setting time zero estimate

```{r}
#plot(x[,15], xlim = c(0, 10))  # plot the 15th trace of the GPR-line
#abline(v = tfb[15], col = "blue")  # first wave break time
```

No change :).

#### Plot a single trace

```{r}
# Plot all samples of the 15 trace of the GPR profile
#plot(x[,15])
# Plot the first 150 samples of the 15th trace of the GPR profile
#plot(xx[,15])
# plot the first 110 samples of the 15th trace of the GPR profile
#plot(x[1:110, 15])
```

```{r}
#plot(x[1:20, 15])  # plot the 15th trace of the GPR-line
# add a green horizontal line
#abline(h = mean(x[1:110, 15]), col = "green")
```

## Time zero corrections

```{r}
#x2 <- time0Cor(xx, method = "pchip")
#plot(x2)
```
## Dewow

```{r}
#x3 <- dewow(x2, type = "Gaussian", w=50)
#plot(x3)

#plot(x3 - x2) 

#plot(x2[,15], col = "blue")      # before dewowing
#lines(x3[,15], col = "red")      # after dewowing
```
## Frequency Filter

Let's have a look at the amplitude-frequency and phase-frequency plot (the spectrum given by the Fourier decomposition):

```{r}
#spec1D(x3)
#x4 <- fFilter(x3, f = c(150, 260), type = "low", plotSpec = TRUE)
```


